\documentclass[12pt,a5paper]{article}

\usepackage{../../LaTeX-Templates/Notes}
\renewcommand{\emph}{\textit}

\usepackage{pgfpages}
\pgfpagesuselayout{2 on 1}[a4paper,landscape,border shrink=5mm]

\title{\vspace{-3em}CP Violation Seminar Notes}
\author{}
\date{}

\begin{document}
\maketitle
\vspace{-4em}
\section{Intro}
\begin{itemize}
    \item Go through first slide, self-explanatory
    \item Still have lots of unanswered questions; some small, some big
    \item Sakharov in 1967 gave his criteria
    \item Yang, Lee, and Wu in 1957 for P, then CP found in 1964 in Kaon mixing
    \item Don't want infinities in our observables
    \item No masses before Higgs, SSB mixes with bosons to give mass, then Yukawa
    \item 2HDM provides a more physical explanation for Yukawa, over convenience
    \item Three different types, focus on II as it has similarities to SM Yukawa
    \item Still have sphalerons, then CP violation and phase sorted
    \item Add Feynman diagrams to amplitudes, can resolve anomalies
    \item If masses are very heavy, effect is negligible and won't change things
\end{itemize}

\section{Fittings}
\begin{itemize}
    \item Started with obvious decays affected 
    \item Leptonic - B, D, Ds, K-pi ratios
    \item Mixing, both B and Bs
    \item $b\to s\gamma$, normalisation constant mention?
    \item $\tan\beta$ could extend higher and lower as we increase $m_{H^+}$, so no real constraint
    \item $m_{H^+}$ has a minimum, but more and more likely as it goes to infinity
    \item Scanning doesn't tell us much, so we need to fit it
    \item Wanted to replicate original paper as best as possible using $\chi^2$, whereas they used R-fit
    \item Scanned to $1.96\sigma$ to correspond to 95\% CL, fitted there, and then found $1\sigma$ region
    \item Some slight differences due to the methods, but reached same minimum and regions look the same
    \item Measurements of new observables since 2010, we want to add these
    \item $B_s\to\mu\mu$ is an interesting one - done so far in large $\tan\beta$ limit so need to do this again
    \item $\mathcal{R}(D^{(*)})$ historically is difficult to fit both at the same time
    \item R(D) follows the same shape as the leptonic paths, but R(D*) is out, is there a way to fix this?
    \item Include R(D) just now and exclude the star, and look for a resolution
    \item Add these to statistical fit, now have new regions and minima
    \item $\tan\beta$ must be $\gtrapprox2$ at $1\sigma$, but at 95\% CL we have the same lack of hard constraint as before
    \item CKM elements will be modified, only really have a big effect on heavier elements though
    \item Chance to improve unitarity, maybe make space for fourth generation
    \item Requires more research, but could have significant changes
\end{itemize}

\section{Extension}
\begin{itemize}
    \item Gen 4, extra phases mean extra CPV, more angles just means more params
    \item Jarlskog, $J=\text{Im}(V_{ud}V_{tb}V_{td}^*V_{ub})\approx3\times10^{-5}$
    \item Extran penguins from heavy quarks
    \item Chiral means SU(2) doublets, i.e. same as before
    \item Neutrino must be $\gtrapprox200\,$GeV I think
\end{itemize}

\newpage
\begin{thebibliography}{99}
\bibitem{a}
O. Deschamps et al, \emph{The Two Higgs Doublet Model of Type II facing flavour physics data}, \href{https://arxiv.org/pdf/0907.5135.pdf}{arxiv:0907.5135}.

\bibitem{c}
Y. Amhis et al [HFLAV], \emph{Averages of b-hadron, c-hadron, and $\tau$-lepton properties as of 2018}, \href{https://arxiv.org/pdf/1909.12524.pdf}{arxiv:1909.12524}.

\bibitem{d}
M. Tanabashi et al [Particle Data Group], Phys. Rev. D98, 030001 (2018) and 2019 update

\bibitem{f}
A. Lenz and G. Tetlalmatzi-Xolocotzi, \emph{Model-independent bounds on new physics effects in non-leptonic tree-level decays of B-mesons}, \href{https://arxiv.org/pdf/1912.07621.pdf}{arxiv:1912.07621}.

\bibitem{g}
CKMfitter Group (J. Charles et al.), Eur. Phys. J. C41, 1-131 (2005) [hep-ph/0406184], updated results and plots available at: \href{http://ckmfitter.in2p3.fr}{http://ckmfitter.in2p3.fr}.

\bibitem{h}
A. Sakharov, \emph{Violation of CP Invariance, C asymmetry, and Baryon Asymmetry of the Universe}, Pisma Zh. Eksp. Teor. Fiz. 5 (1967) 32 [JETP Lett. 5 (1967) 24] [Sov. Phys. Usp. 34 (1991) 392] [Usp. Fiz. Nauk 161 (1991) 61].

\bibitem{i}
L. Di Luzio, M. Kirk, A. Lenz, T. Rauh, \emph{$\Delta M_s$ theory precision confronts flavour anomalies}, \href{https://arxiv.org/pdf/1909.11087.pdf}{arxiv:1909.11087}.

\bibitem{j}
S. Aoki et al [FLAG], \emph{FLAG Review 2019}, \href{https://arxiv.org/pdf/1902.08191.pdf}{arxiv:1902.08191}.

\bibitem{r}
A. Lenz, \emph{Constraints on a Fourth Generation of Fermions from Higgs Boson Searches}, Advances in High Energy Physics \textbf{2013}, 1 (2013).

\bibitem{s}
G.C. Branco et al, \emph{Theory and phenomenology of two-Higgs-doublet models}, \href{https://arxiv.org/pdf/1106.0034.pdf}{arxiv:1106.0034}.

\bibitem{t}
W. Altmannshoger et al, \emph{Addressing $R_{D^{(*)}}. R_{K^{(*)}}$ muon $g-2$ and ANITA anomalies in a minimal $R$-parity violating supersymmetric framework}, \href{https://arxiv.org/pdf/2002.12910.pdf}{arxiv:2002.12910}.
\end{thebibliography}

\end{document}

